## Project Overview
#This project looks at the block lots that are within the downtown area. Using a shapefile of the downtown area, I will use st_intersect to intersect the blocks within the downtown area.

## Libraries
#Loading the libraries that are needed.

```{r libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(r4OPI)
library(sf)
library(here)
library(fastmap)
library(tidycensus)
library(lubridate)
library(Microsoft365R)
library(AzureGraph)
library(DBI)
library(tibble)
library(janitor)
library(odbc)
library(stringr)
```

## Reading in the datasets
#Reading in the shapefiles that are needed to complete the analysis.

```{r datasets}
dntw <- st_read(here("shapefiles", "downtown.shp"))
art <- read.csv(here("results", "all_art_data.csv"))
```

## Conversion and Spatial Join
Changing the projection for the dataset to match the downtown boundary. Do a st_intersection to make sure that we are only looking at data that is within the downtown boundary.

```{r analysis}
# Convert to sf object
art_sf <- st_as_sf(art, coords = c("longitude", "latitude"), crs = 4326)

# Transform downtown boundary to same CRS
dntw <- st_transform(dntw, 4326)

# Spatial join: filter crimes within downtown boundary
dntw_art <- st_intersection(art_sf, dntw)

# Create exportable data frame with WKT and lat/lon
dntw_art_wkt <- dntw_art %>%
  mutate(wkt = st_as_text(geometry)) %>%
  st_drop_geometry() %>%
  mutate(
    geometry_clean = str_remove_all(wkt, "POINT \\(|\\)"),
    longitude = as.numeric(str_extract(geometry_clean, "^-?\\d+\\.\\d+")),
    latitude = as.numeric(str_extract(geometry_clean, "(?<= )-?\\d+\\.\\d+$"))
  )

# Drop geometry and convert to a plain dataframe
dntw_art_wkt <- st_drop_geometry(dntw_art_wkt)
```
## Write out the data
I want to write out a shapefile and a xlsx file for mapping in the dashboard.

```{r writeout}
st_write(dntw_art, here("shapefiles", "art_dma.shp"), append = F)
writexl::write_xlsx(dntw_art_wkt, here("results", "dntw_art_wkt.xlsx")) 
```

